### 2013-09-20 evaluation/paper.tex
blabla for experiments...

\subsection{Sequence Labeling (OCR)}
A classical application of structured prediction is sequence labeling.
We choose the ``OCR'' dataset introduced in the seminal work of \citet{taskar2003max}.
Each input consists of the segmented handwritten letters of a word in lower case. The task is to classify
all letters in a word, that is assign each segmented input letter one of the
classes ``a'' to ``z''. As the first letter of each word was capitalized, these
were removed by \citet{taskar2003max}, leading to somewhat odd-looking
labels. The words are between \ldots and \ldots letters long, and each letter
is represented as a binary image of size \ldots.
We use a simple chain model with a single constant pairwise feature.
This means the unary potential has \ldots parameters, one for each input
feature and output class. The pairwise potential consists of a matrix of
transition potentials with $26 x 26=676$ entries.
It is well-known that efficient exact inference in chains is possible using
message passing algorithms. 
%We use the dynamic programming algorithm
%implemented in \textsc{OpenGM}.

@@

\section{Experiments}
We compare the following algorithms on the above models:
\begin{itemize}
    \item Stochastic Subgradient Descent using the Pegasos schedule: %TODO
    \item Stochastic Subgradient Descent using a momentum heuristic:
    %\item Stochastic Subgradient Descent using a momentum heuristic: AVERAGING
    %\item Stochastic Subgradient Descent using a momentum heuristic: AVERAGING
    \item The $1$-slack cutting plane algorithm without constraint caching.
    \item The $1$-slack cutting plane algorithm with constraint caching. For
            each sample, the last $50$ inference results are stored.
            Details of the caching strategy can be found in Chapter~\ref{ch:exact_learning}.
            %TODO
    \item The $n$-slack cutting plane algorithm, where the QP is solved after each training.
    \item The $n$-slack cutting plane algorithm, where the QP is solved every 100 training samples.
    \item The SZLJSP algorithm.
\end{itemize}
All algorithm take a $C$ parameter, which we adjusted on a fully trained model
on a validation set (experiments not reported here) and held constant for all models.
We found, however, that the algorithms and models are quite robust to the choice of $C$ within
one or two orders of magnitude.
As stopping criterion, we used a duality gap of $0.1$ when possible, and a pre-defined
number of iterations for the subgradient algorithms.

Our ultimate evaluation criterion is how fast the learning algorithms converge,
and how robust they are to approximate inference.  To quantify our goals, we
track primal suboptimality and training set error during learning, as well as
final error on the test set.
We report suboptimality as a function of runtime, and as a function of passes over the training set.
Both are important to practitioners, as they give important insight into the workins of the algorithm.
The actual runtime is certainly the most important factor, but also highly influenced by implementation details
and properties of the dataset. We are particularly interested in cases where inference is highly non-trivial.
In these cases, inference

>>>>

\subsection{Sequence Labeling (OCR)}
A classical application of structured prediction is sequence labeling.
We choose the ``OCR'' dataset introduced in the seminal work of \citet{taskar2003max}.
Each input consists of the segmented handwritten letters of a word in lower case. The task is to classify
all letters in a word, that is assign each segmented input letter one of the
classes ``a'' to ``z''. As the first letter of each word was capitalized, these
were removed by \citet{taskar2003max}, leading to somewhat odd-looking
labels. The words are between \ldots and \ldots letters long, and each letter
is represented as a binary image of size \ldots.
We use a simple chain model with a single constant pairwise feature.
This means the unary potential has \ldots parameters, one for each input
feature and output class. The pairwise potential consists of a matrix of
transition potentials with $26 x 26=676$ entries.
It is well-known that efficient exact inference in chains is possible using
message passing algorithms.

@@

\section{Experiments}
We compare the following algorithms on the above models:
\begin{itemize}
    \item Stochastic Subgradient Descent using the Pegasos schedule: %TODO
    \item Stochastic Subgradient Descent using a momentum heuristic:
    %\item Stochastic Subgradient Descent using a momentum heuristic: AVERAGING
    %\item Stochastic Subgradient Descent using a momentum heuristic: AVERAGING
    \item The $1$-slack cutting plane algorithm without constraint caching.
    \item The $1$-slack cutting plane algorithm with constraint caching. For
            each sample, the last $50$ inference results are stored.
            Details of the caching strategy can be found in Chapter~\ref{ch:exact_learning}.
            %TODO
    \item The $n$-slack cutting plane algorithm, where the QP is solved after each training.
    \item The $n$-slack cutting plane algorithm, where the QP is solved every 100 training samples.
    \item The SZLJSP algorithm.
\end{itemize}
All algorithm take a $C$ parameter, which we adjusted on a fully trained model
on a validation set (experiments not reported here) and held constant for all models.
We found, however, that the algorithms and models are quite robust to the choice of $C$ within
one or two orders of magnitude.
As stopping criterion, we used a duality gap of $0.1$ when possible, and a
pre-defined number of iterations for the subgradient algorithms. It is worth
noting that the quadratic programming based algorithms have additional
hyper-parameters that we do not discuss here in detail, such as the threshold
for removing a constraint as inactive, how often inactive constraints are
removed, and parameters of the underlying QP solver. On the other hand, the
SZLJSP, for example, has no hyper-parameters except for the stopping criterion.

Our ultimate evaluation criterion is how fast the learning algorithms converge,
and how robust they are to approximate inference.  To quantify our goals, we
track primal suboptimality and training set error during learning, as well as
final error on the test set.
We report suboptimality as a function of runtime, and as a function of passes
over the training set.  Both are important to practitioners, as they give
important insight into the workins of the algorithm.  The actual runtime is
certainly the most important factor, but also highly influenced by
implementation details and properties of the dataset. We are particularly
interested in cases where inference is highly non-trivial, making inference the
dominating factor of runtime.
We define one pass over the dataset as calling prediction once for each sample.
This way, we can get a clear picture how learning times with complexity of the
inference task.

\subsection{Experiments using Exact Inference}
In this section, we present results on multi-class classification, sequence
labeling and multi-label prediction with a tree-structured model. In these
tasks, exact inference is possible, and we can compute the exact objective of
the various algorithms easily. We use the dynamic programming algorithm
implemented in \textsc{OpenGM} for experiments

\subsection{Experiments using Approximate Inference}
For the remaining tasks of multi-label classification with the full graph, the
snakes dataset and image segmentation, exact inference is usually not possible.

We use two different approximate inference algorithms, fusion moves, a fast
local search procedure, and AD$^3$, a dual-subgradient method to solve the LP
relaxation of the inference problem.
Evaluation of algorithms where exact inference is not possible is much harder,
as it is usually not possible to evaluate the exact objective. When using AD$^3$,
we can still consider the relaxed task, which will be solved exactly in the
majority of cases (AD$^3$ sometimes fails to find the primal solution to the LP
relaxation). %TODO is this happening?
When using fusion moves, there is no obvious interpretation of the produced
primal objective, other than that it provides a lower bound of the actual
objective. Nevertheless, we find it informative to analyze the behavior of this lower bound.

For both inference algorithms, we also evaluate the predictive performance on
the training set.  We explicitly do not consider the relaxed problem
here---instead we round possible fractional results.
While the training error does not directly reflect the objective, it provides
a measure of how effective the ``prediction machine'' given by the learned model
together with the inference algorithm is.

\section{Discussion}
